<!-- question-type: inclass -->
### Exercise 7: Putting the plots together

**(a).** Use the code below to combine the plots for the three exercises above. Replace `PLOT_ONE`, `PLOT_TWO`, and `PLOT_THREE` with the plots you created in Exercises 5, 6, and 7.

```{r}
#| eval: false
PLOT_ONE /    
    (PLOT_TWO | PLOT_THREE) + 
    plot_layout(guides = "collect") & 
    theme(legend.position = "bottom")
```

**(b).** Save this combined plot as a PDF file using the `ggsave()` function. You can specify the file name and dimensions using the `filename` and `width` and `height` arguments.

```{r}
#| eval: false
ggsave("YOUR_FILE_NAME", width = 12, height = 8)
```

<!-- BEGIN PROFILE:r-teaching-guide -->
::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective** 
Students should:

- XXXXX

✅   **Core Concepts to Highlight**

List them here


💬 **Suggested In-Class Prompts** (if needed)

List as needed

📌 **Common Misunderstandings**

List as needed

:::

:::

:::
<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->
::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

Here’s the explanation and code:

```{r}
print("Hello, world!")
```
:::

:::

:::
<!-- END PROFILE:r-solutions -->