<!-- question-type: prepare -->
### Exercise 2: Visualizing the distribution of Prices by Dwelling Type

By the end of this exercise, your plot should look similar to this one:

```{r}
#| fig-width: 5
#| fig-height: 5
#| fig-align: "center"
#| echo: false

housing %>%
    ggplot(aes(x = price, 
               fill = type)
           ) +
    geom_histogram(bins = 50) +
    # Natural log scale for x-axis with meaningful breaks
    scale_x_continuous(
        labels = scales::dollar,
    ) +
    labs(x = "Price", 
         y = "Density within Type", 
         title = "Prices by Dwelling Type"
         ) + 
    theme(
        axis.text.x = element_text(angle = 55, hjust = 1),
    ) +
    facet_wrap(~ type)
```

**(a).** Why is a histogram useful for understanding price distributions? What insights can we gain from plotting price distributions separately for each dwelling type?

:::{.callout-tip title="What is a Histogram?" collapse=true}
A **histogram** is a visualization that represents the **distribution of numerical data** by dividing values into bins and counting the number of observations in each bin. Unlike a bar plot, which displays **categorical data**, a histogram is used for **continuous variables** like price, age, or distance.

Histograms help identify **patterns** in data, such as **skewness, outliers, and central tendencies**, making them a crucial tool for understanding how values are distributed in a dataset.
:::


**(b).** Use the starter code below to create a basic histogram of house prices. Replace `YOUR_VARIABLE_NAME` with the correct variable.

```{r}
#| eval: false
ggplot(housing, 
       aes(x = YOUR_VARIABLE_NAME)
       ) +
    geom_histogram(bins = 50)
```

**(c).** Extend the plot above by adding labels to the x-axis, y-axis, and title using the labs() function.

```{r}
#| eval: false
ggplot(housing, 
       aes(x = YOUR_VARIABLE_NAME)
       ) +
    geom_histogram(bins = 50) +
    labs(x = "YOUR_X_AXIS_LABEL", 
         y = "YOUR_Y_AXIS_LABEL", 
         title = "YOUR_TITLE"
         )
```

**(d).** Modify the x-axis so that prices are displayed in dollar format by adding `scale_x_continuous(labels = scales::dollar).` We have rotated the axis labels to make the numbers easier to read.

```{r}
#| eval: false

ggplot(housing, 
       aes(x = price)
       ) +
    geom_histogram(bins = 50) +
    YOUR_CODE_HERE +
    labs(x = "YOUR_X_AXIS_LABEL", 
         y = "YOUR_Y_AXIS_LABEL", 
         title = "YOUR_TITLE"
         ) +
    theme(
        axis.text.x = element_text(angle = 55, hjust = 1),
    )
```

**(e).** Add `fill = type` inside `aes()` to color the histogram by dwelling type and then create subplots by dwelling type.

```{r}
#| eval: false
ggplot(housing, 
       aes(x = price, 
           YOUR_CODE_HERE
           )
       ) +
    geom_histogram(bins = 50) +
    YOUR_CODE_HERE +
    labs(x = "YOUR_X_AXIS_LABEL", 
         y = "YOUR_Y_AXIS_LABEL", 
         title = "YOUR_TITLE"
         ) +
    theme(
        axis.text.x = element_text(angle = 55, hjust = 1),
    ) +
    YOUR_CODE_HERE
```

**(f).** What does the histogram tell you about price differences between dwelling types?


<!-- BEGIN PROFILE:r-teaching-guide -->
::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective** 
Students should:

- XXXXX

✅   **Core Concepts to Highlight**

List them here


💬 **Suggested In-Class Prompts** (if needed)

List as needed

📌 **Common Misunderstandings**

List as needed

:::

:::

:::
<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->
::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

Here’s the explanation and code:

```{r}
print("Hello, world!")
```
:::

:::

:::
<!-- END PROFILE:r-solutions -->