<!-- question-type: prepare -->
### Exercise 1: Plotting Number of Listings by Region

By the end of this exercise, your plot should look similar to this one:

```{r}
#| fig-width: 5
#| fig-height: 5
#| fig-align: "center"
#| echo: false

ggplot(housing, 
       aes(x = regionname)
       ) +
    geom_bar() +
    labs(x = "Region", 
         y = "Frequency", 
         title = "Number of Listings by Region"
         ) +
    theme(
        axis.text.x = element_text(angle = 25, hjust = 1),
    )
```


**(a).** If you were a real estate investor or city planner, why would knowing the number of listings by region be valuable? What decisions could be influenced by this visualization?

**(b).** Use the starter code below to create a first version of the bar plot. Replace `YOUR_VARIABLE_NAME` with the appropriate variable name from the dataset.

:::{.callout-tip title="What is a Bar Plot?" collapse = "true"}
A **bar plot** is a graphical representation of categorical data, where each category is represented by a bar whose height reflects its frequency or proportion. It is commonly used to compare counts across different groups, making it easy to identify the most and least common categories in a dataset. In business and research, bar plots help visualize trends, distributions, and key differences in data at a glance.
:::

```{r}
#| eval: false
ggplot(housing, 
       aes(x = YOUR_VARIABLE_NAME)
       ) +
    geom_bar()
```

**(c).** Extend the plot above by adding labels to the x-axis, y-axis, and title. Use the `labs()` function to add these labels. The code below also rotates the axis labels by 25 degrees to improve readability.

```{r}
#| eval: false
ggplot(housing, 
       aes(x = YOUR_VARIABLE_NAME)
       ) +
    geom_bar() +
    labs(x = "YOUR_X_AXIS_LABEL", 
         y = "YOUR_Y_AXIS_LABEL", 
         title = "YOUR_TITLE"
         ) +
    theme(
        axis.text.x = element_text(angle = 25, hjust = 1),
    )
```

**(d).** What patterns do you notice in the number of listings? Are certain regions overrepresented or underrepresented? How might this affect housing supply and pricing? 

<!-- BEGIN PROFILE:r-teaching-guide -->
::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective** 
Students should:

- Learn how to create a bar plot using ggplot2 to display frequency of a categorical variable
- Apply basic plot customizations using `labs()`
- Begin interpreting data distributions and considering real-world implications


✅   **Core Concepts to Highlight**

- Bar plots show frequency counts of categorical variables
- `geom_bar()` uses the count of rows in each category by default
- The `aes(x = regionname)` maps the variable to the x-axis
- `labs()` is used to add informative axis labels and a title
- Interpretation connects visual patterns to business context (e.g. supply, market activity)


💬 **Suggested In-Class Prompts** (if needed)

NA

📌 **Common Misunderstandings**

- Confusing `geom_bar()` (which counts observations) with `geom_col()` (which uses values)
- Using the wrong variable in `aes(x = ...)` — e.g. numeric instead of categorical
- Assuming more listings = better opportunities, without thinking about demand
- Misinterpreting the y-axis — it's count of rows, not price or square meters

:::

:::

:::
<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->
::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

**(a). Why is this information valuable to real estate investors or city planners?**

Knowing the number of listings by region helps real estate investors identify which areas have a large housing supply, suggesting more opportunities to buy or sell. For city planners, it gives insight into regional activity and potential infrastructure or zoning needs. For example:

- A region with many listings might signal high development or turnover.
- A region with few listings might suggest limited availability or less desirability, or that it is mostly owner-occupied.
- Investors may use this to target areas with more competition (supply) or fewer listings (scarcity).
- City planners might use it to anticipate demand for transport, utilities, or amenities.

NOTE: this is not the only correct answer to this question.

**(b). Starter code with correct variable name**

The variable we want on the x-axis is regionname. Here's the updated code:

```{r}
ggplot(housing, 
       aes(x = regionname)
       ) +
    geom_bar()
```

**(c). Extended version with labels and rotated axis text**

```{r}
ggplot(housing, 
       aes(x = regionname)
       ) +
    geom_bar() +
    labs(
        x = "Region", 
        y = "Number of Listings", 
        title = "Number of Listings by Region"
    ) +
    theme(
        axis.text.x = element_text(angle = 25, hjust = 1)
    )
```

**(d)**

From the plot, we can see several clear patterns:

- Northern Metro and Southern Metro have the highest number of listings
- South-East Metro has the fewest listings
- Western Metro is also highly active, with nearly as many listings as the Northern and Southern regions.
Eastern Metro has moderate activity.

(possible) Interpretation:

- The uneven distribution of listings suggests that some regions (e.g., South-East Metro) may have limited housing supply, while others (e.g., Northern and Southern Metro) are more active markets.
- This can affect pricing dynamics — high-supply regions may offer more choice and competition, while low-supply areas could see rising prices due to scarcity.

:::

:::

:::
<!-- END PROFILE:r-solutions -->
