<!-- question-type: prepare -->
### Exercise 3: The Price - Distance Relationship

By the end of this exercise, your plot should look similar to this one:

```{r}
#| fig-width: 5
#| fig-height: 5
#| fig-align: "center"
#| echo: false
ggplot(housing, 
       aes(x = distance, y = price)
       ) +
    geom_point(alpha = 0.05) +
    geom_smooth(method = "lm",
                se = FALSE, 
                linewidth = 1
                ) +
    scale_y_continuous(labels = scales::dollar) +
    labs(x = "Distance to CBD (km)", 
         y = "Price", 
         title = "House Price vs. Distance"
         )
```
**(a).** Why might we expect a relationship between price and distance to the CBD?

**(b).** Use the starter code below to build a scatter plot of **price vs. distance**, replacing `YOUR_VARIABLE_NAME` with the correct column names.

::: {.callout-tip title="What is a Scatter Plot?" collapse=true}
A **scatter plot** is used to visualize the relationship between two continuous variables by plotting individual data points. Each dot represents one observation, helping identify **patterns, clusters, and trends**. In this case, it allows us to explore how **house prices change with distance**.
:::

```{r}
#| eval: false
ggplot(housing, 
       aes(x = YOUR_VARIABLE_NAME, y = YOUR_VARIABLE_NAME)
       ) +
    geom_point()
```

**(c).** Since we have a large number of data points, many overlap, making it difficult to distinguish individual observations. Modify the `geom_point()` function to reduce over-plotting by adjusting the `alpha` value. Experiment with different values (e.g., 0.1, 0.05, 0.01) and describe how each affects the visualization.

```{r}
#| eval: false
ggplot(housing, 
       aes(x = YOUR_VARIABLE_NAME, y = YOUR_VARIABLE_NAME)
       ) +
    geom_point(alpha = YOUR_NUMBER)
```

**(d).** We can better understand the relationship by adding a statistical transformation to the plot. Complete the `geom_smooth()` function call to overlay a straight line over the data. The `se = FALSE` argument removes the confidence interval around the line.

```{r}
#| eval: false
ggplot(housing, 
       aes(x = YOUR_VARIABLE_NAME, 
           y = YOUR_VARIABLE_NAME)
       ) +
    geom_point(alpha = YOUR_NUMBER) +
    geom_smooth(method = YOUR_METHOD, 
                se = FALSE)
```

**(e).** Finally, add labels to the x-axis, y-axis, and title using the `labs()` function. Adjust the x- and y-axis scales as you deem appropriate.

```{r}
#| eval: false
ggplot(housing, 
       aes(x = YOUR_VARIABLE_NAME, y = YOUR_VARIABLE_NAME)
       ) +
    geom_point(alpha = YOUR_NUMBER) +
    geom_smooth(method = YOUR_METHOD, 
                se = FALSE) +
    scale_y_continuous(YOUR_CODE) +
    labs(x = "YOUR_LABEL", 
         y = "YOUR_LABEL", 
         title = "YOUR_TITLE"
         )
```

**(f).** What does the scatter plot reveal about the relationship between house prices and distance to the CBD? How does the line help interpret this relationship?


<!-- BEGIN PROFILE:r-teaching-guide -->
::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective** 
Students should:

- XXXXX

✅   **Core Concepts to Highlight**

List them here


💬 **Suggested In-Class Prompts** (if needed)

List as needed

📌 **Common Misunderstandings**

List as needed

:::

:::

:::
<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->
::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

Here’s the explanation and code:

```{r}
print("Hello, world!")
```
:::

:::

:::
<!-- END PROFILE:r-solutions -->