<!-- question-type: prepare -->
### Exercise 1: Plotting Number of Listings by Region

By the end of this exercise, your plot should look similar to this one:

```{r}
#| fig-width: 5
#| fig-height: 5
#| fig-align: "center"
#| echo: false

ggplot(housing, 
       aes(x = regionname)
       ) +
    geom_bar() +
    labs(x = "Region", 
         y = "Frequency", 
         title = "Number of Listings by Region"
         ) +
    theme(
        axis.text.x = element_text(angle = 25, hjust = 1),
    )
```


**(a).** If you were a real estate investor or city planner, why would knowing the number of listings by region be valuable? What decisions could be influenced by this visualization?

**(b).** Use the starter code below to create a first version of the bar plot. Replace `YOUR_VARIABLE_NAME` with the appropriate variable name from the dataset.

:::{.callout-tip title="What is a Bar Plot?" collapse = "true"}
A **bar plot** is a graphical representation of categorical data, where each category is represented by a bar whose height reflects its frequency or proportion. It is commonly used to compare counts across different groups, making it easy to identify the most and least common categories in a dataset. In business and research, bar plots help visualize trends, distributions, and key differences in data at a glance.
:::

```{r}
#| eval: false
ggplot(housing, 
       aes(x = YOUR_VARIABLE_NAME)
       ) +
    geom_bar()
```

**(c).** Extend the plot above by adding labels to the x-axis, y-axis, and title. Use the `labs()` function to add these labels. The code below also rotates the axis labels by 25 degrees to improve readability.

```{r}
#| eval: false
ggplot(housing, 
       aes(x = YOUR_VARIABLE_NAME)
       ) +
    geom_bar() +
    labs(x = "YOUR_X_AXIS_LABEL", 
         y = "YOUR_Y_AXIS_LABEL", 
         title = "YOUR_TITLE"
         ) +
    theme(
        axis.text.x = element_text(angle = 25, hjust = 1),
    )
```

**(d).** What patterns do you notice in the number of listings? Are certain regions overrepresented or underrepresented? How might this affect housing supply and pricing? 

<!-- BEGIN PROFILE:r-teaching-guide -->
::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective** 
Students should:

- XXXXX

✅   **Core Concepts to Highlight**

List them here


💬 **Suggested In-Class Prompts** (if needed)

List as needed

📌 **Common Misunderstandings**

List as needed

:::

:::

:::
<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->
::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}

Here’s the explanation and code:

```{r}
print("Hello, world!")
```
:::

:::

:::
<!-- END PROFILE:r-solutions -->
